---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# audrey

<!-- badges: start -->
<!-- badges: end -->

audrey serves as a client to [OpenAI Whisper](https://github.com/openai/whisper), a general-purpose speech recognition model is trained on a large dataset of diverse audio. It can perform multilingual speech recognition, speech translation, and language identification.


## Installation

You can install the development version of audrey from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("howardbaek/audrey")
```

Importantly, you need to download Whisper with the following command:

```
pip install -U openai-whisper
```

You also need the command-line tool `ffmpeg` on your system:

```
# on Ubuntu or Debian
sudo apt update && sudo apt install ffmpeg

# on Arch Linux
sudo pacman -S ffmpeg

# on MacOS using Homebrew (https://brew.sh/)
brew install ffmpeg

# on Windows using Chocolatey (https://chocolatey.org/)
choco install ffmpeg

# on Windows using Scoop (https://scoop.sh/)
scoop install ffmpeg
```

For more information, refer to the Whisper's [Setup](https://github.com/openai/whisper#setup) documentation.


## Usage

### `transcribe()`

Convert the input audio file into written text using speech recognition, while preserving the language of the original audio:

```{r}
library(audrey)

transcribe(system.file("extdata", "sample-english1.mp3",  package = "audrey"),
           output_dir = ".")
```


### `translate()`

Provide an English translation of the input audio file that is originally spoken in a non-English language:

```{r}
# Korean to English
translate(system.file("extdata", "sample-korean.wav",  package = "audrey"),
          audio_lang = "Korean", output_dir = ".")
```


## Acknowledgements

- OpenAI [Whisper model](https://github.com/openai/whisper)
- Source of audio files: https://commonvoice.mozilla.org/en/datasets
